---
title: "Data Science logs"
author: "Leonardo Collado-Torres"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook: default
---

# Overview {-}

This website contains the public logs for the Data Science guidance sessiones carried out by the [**R/Bioconductor-powered Team Data Science**](https://lcolladotor.github.io/bioc_team_ds) at [LIBD](https://www.libd.org/).

## DSgs-guide team members {-}

* [Arta Seyedian](https://github.com/aseyedia)
* [Joshua M. Stolz](https://github.com/joshstolz)
* [Louise Huuki](https://github.com/lahuuki)
* [Nicholas J. Eagles](https://github.com/Nick-Eagles)
* [Madhavi Tippani](https://github.com/madhavitippani)

This book was last updated on `r Sys.time()`.

## R session information {-}

Details on the R version used for making this book. The source code is available at [`lcolladotor/DSgs_logs`](https://github.com/lcolladotor/DSgs_logs).

```{r session_info_chunk, eval = FALSE}
## Load the package at the top of your script
library("sessioninfo")

## Reproducibility information
print('Reproducibility information:')
Sys.time()
proc.time()
options(width = 120)
session_info()
```

```{r session_info, echo = FALSE}
<<session_info_chunk>>
```
