---
title: "Data Science guidance session logs"
author: "Leonardo Collado-Torres"
site: bookdown::bookdown_site
apple-touch-sin: "icon_192.png"
apple-touch-icon-size: 192
favicon: "icon_32.png"
github-repo: "lcolladotor/dsgs_logs"
documentclass: book
output:
  bookdown::gitbook:
    includes:
      after_body: map_and_ga.html
    css: "style.css"
---

# Overview {-}

This website contains the public logs for the [Data Science guidance sessions (**DSgs**)](https://lcolladotor.github.io/bioc_team_ds/data-science-guidance-sessions.html).

## DSgs-guides {-}

* [Cynthia S. Cardinault](https://github.com/cyntsc)
* [Louise A. Huuki-Myers](https://github.com/lahuuki)
* [Madhavi Tippani](https://github.com/madhavitippani)
* [Nicholas J. Eagles](https://github.com/Nick-Eagles)

_Former guides:_

* [Abby Spangler](https://github.com/abspangler13)
* [Arta Seyedian](https://github.com/aseyedia)
* [Joshua M. Stolz](https://github.com/joshstolz)

## Graphs {-}

```{r "load_libraries", echo = FALSE, message = FALSE, warning = FALSE}
## Packages used in the book
library("ggplot2")
library("lubridate")
library("dplyr")
library("plotly")
library("gt")
library("here")
```


Below we see the number of [DSgs](https://lcolladotor.github.io/bioc_team_ds/data-science-guidance-sessions.html) sessions for each of the guides across time. You can mouse-over each point to see the data, or click on each guide's name to hide/show their information. The data is filtered to show only active DSgs guides.

```{r "graph_by_guide", echo = FALSE, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 8}
load(here::here("logs_data.Rdata"))

## Clean up a bit
logs_data$date <- as.Date(logs_data$date)
logs_data$week <- isoweek(logs_data$date)
logs_data$year <- year(logs_data$date)


## Drop NAs if any on the date
logs_data <- logs_data[!is.na(logs_data$date), ]

top_types <- sort(table(logs_data$type), decreasing = TRUE)

## Summarise the data to get the number of sessions per week on a given year
by_guide_summary <- summarise(group_by(logs_data, week, year, guide_name), "number"=n())

## Plot by day of the year
p <- ggplot(filter(by_guide_summary, !guide_name %in% c("Abby", "Josh", "Arta", "Ryan", "Hedia")) , aes(
    x = week,
    y = number,
    color = guide_name,
    group = guide_name
)) +
    geom_point() +
    geom_line() +
    xlab("Week of the year") +
    ylab("Number of sessions") +
    scale_y_continuous(
        breaks = seq(0, max(by_guide_summary$number) + 1, by = 1),
        limits = c(0, max(by_guide_summary$number) + 1)) +
    labs(color = "Guide") +
    facet_grid(year ~ .) +
    theme_dark(base_size = 20) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    scale_color_brewer(palette = "Accent")
ggplotly(p)
```

As a team, this is the overall number of help requests we have completed over time grouped by day and year.

```{r "graph_total", echo = FALSE, warning = FALSE, message = FALSE}
## Plot by week of the year ignoring guide
by_total <-
    summarise(group_by(logs_data, week, year, day = factor(
        weekdays(logs_data$date, TRUE), levels = rev(c(
            "Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"
        ))
    )), hours = n())

## From https://vuorre.netlify.app/post/2016/03/24/github-style-waffle-plots-in-r/
## edited "Hours" to "Sessions for the legend name
gh_waffle <- function(data, pal = "D", dir = -1) {
  p <- ggplot(data, aes(x = week, y = day, fill = hours)) +
    scale_fill_viridis_c(
      name = "Sessions",
      option = pal, # Variable color palette
      direction = dir, # Variable color direction
      na.value = "grey90",
      limits = c(0, max(data$hours))
    ) +
    geom_tile(color = "white", linewidth = 0.7) +
    facet_wrap("year", ncol = 1) +
    scale_x_continuous(
      expand = c(0, 0),
      breaks = seq(1, 52, length = 12),
      labels = c(
        "Jan", "Feb", "Mar", "Apr", "May", "Jun",
        "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"
      )
    ) +
    theme_linedraw(base_family = "Helvetica") +
    theme(
      axis.title = element_blank(),
      axis.ticks = element_blank(), 
      axis.text.y = element_text(size = 7),
      panel.grid = element_blank(),
      legend.position = "bottom",
      aspect.ratio = 1/7,
      legend.key.width = unit(1, "cm"),
      strip.text = element_text(hjust = 0.00, face = "bold", size = 12)
    )

  print(p)
}

gh_waffle(by_total, pal = "A")

```

These graphs are partially based on [`lcolladotor/mphtasessions`](https://github.com/lcolladotor/mphtasessions/blob/gh-pages/index.Rmd) and [_GitHub-style waffle plots in R_](https://vuorre.netlify.app/post/2016/03/24/github-style-waffle-plots-in-r/).

## Full logs {-}

Here you an explore the full logs. The name of the person asking the question(s) is not displayed for privacy.

The idea is that this information could be useful for people who have similar questions, as well as for DSgs guides who want to re-use material from previous answers when helping someone.

```{r "logs_table"}
logs_data$guide <- logs_data$guide_name
gt::gt(logs_data[, c("date", "guide", "help_request", "public_notes")]) |>
    gt::cols_width(
        date ~ gt::px(120),
        guide ~ gt::px(100),
        help_request ~ gt::px(200),
        public_notes ~ gt::px(680)
    ) |>
    gt::fmt_markdown(columns = c("help_request", "public_notes")) |>
    gt::tab_options(
        ihtml.active = TRUE,
        ihtml.use_search = TRUE,
        ihtml.use_filters = TRUE,
        ihtml.use_resizers = TRUE,
        table.width = gt::px(1200)
    )
```



## R session information {-}

Details on the R version used for making this book. The source code is available at [`lcolladotor/DSgs_logs`](https://github.com/lcolladotor/DSgs_logs).

```{r session_info_chunk}
## Packages used in the book
library("ggplot2")
library("lubridate")
library("dplyr")
library("plotly")
library("here")

## Load the package at the top of your script
library("sessioninfo")

## Reproducibility information
print('Reproducibility information:')
Sys.time()
proc.time()
options(width = 120)
session_info()
```

This book was last updated on `r Sys.time()`.
