---
title: "Data Science guidance session logs"
author: "Leonardo Collado-Torres"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook: default
---

# Overview {-}

This website contains the public logs for the Data Science guidance sessiones carried out by the [**R/Bioconductor-powered Team Data Science**](https://lcolladotor.github.io/bioc_team_ds) at [LIBD](https://www.libd.org/).

## DSgs-guide team members {-}

* [Arta Seyedian](https://github.com/aseyedia)
* [Joshua M. Stolz](https://github.com/joshstolz)
* [Louise Huuki](https://github.com/lahuuki)
* [Nicholas J. Eagles](https://github.com/Nick-Eagles)
* [Madhavi Tippani](https://github.com/madhavitippani)

This book was last updated on `r Sys.time()`.

## R session information {-}

Details on the R version used for making this book. The source code is available at [`lcolladotor/DSgs_logs`](https://github.com/lcolladotor/DSgs_logs).

```{r session_info_chunk, eval = FALSE}
## Packages used in the book
library("ggplot2")
library("lubridate")
library("dplyr")
library("here")

## Load the package at the top of your script
library("sessioninfo")

## Reproducibility information
print('Reproducibility information:')
Sys.time()
proc.time()
options(width = 120)
session_info()
```

```{r session_info, echo = FALSE}
<<session_info_chunk>>
```

# Graphs

Below we see the number of [DSgs](https://lcolladotor.github.io/bioc_team_ds/data-science-guidance-sessions.html) sessions across weeks for each of the guides for each type of help/guidance request over the last four weeks.

```{r "graph_by_guide", echo = FALSE, warning = FALSE, message = FALSE}
load(here::here("logs_data.Rdata"))

## Clean up a bit
logs_data$date <- as.Date(logs_data$date)
logs_data$week <- isoweek(logs_data$date)
logs_data$year <- year(logs_data$date)

## Summarise the data to get the number of sessions per week on a given year
by_guide_summary <- summarise(group_by(logs_data, week, year, guide_name, type), "number"=n())

## Plot by day of the year
# ggplot(by_guide_summary , aes(
#     x = paste0(year, '-', week),
#     y = number,
#     color = guide_name,
#     group = guide_name
# )) +
#     geom_point() +
#     geom_line() +
#     xlab("Week of the year") +
#     ylab("Number of sessions") +
#     scale_y_continuous(
#         breaks = seq(0, max(by_guide_summary$number) + 1, by = 1),
#         limits = c(0, max(by_guide_summary$number) + 1)) +
#     labs(color = "Guide") +
#     facet_grid(type ~ .) +
#     theme_bw(base_size = 20)

last_four <- subset(by_guide_summary, week > (isoweek(Sys.time()) - 4) & year == year(Sys.time()))
ggplot(last_four, aes(
    x = paste0(year, '-', week),
    y = number,
    color = guide_name,
    group = guide_name
)) +
    geom_point() +
    geom_line() +
    xlab("Week of the year") +
    ylab("Number of sessions") +
    scale_y_continuous(
        breaks = seq(0, max(last_four$number) + 1, by = 1),
        limits = c(0, max(last_four$number) + 1)) +
    labs(color = "Guide") +
    facet_grid(type ~ .) +
    theme_dark(base_size = 20)
```

As a team, we can see the number of requests we've addressed over the weeks.

```{r "graph_week_total", echo = FALSE, warning = FALSE, message = FALSE}
## Plot by week of the year ignoring guide, for each type
by_week <- summarise(group_by(by_guide_summary, week, year, type), number = sum(number))
ggplot(by_week, aes(
    x = paste0(year, '-', week),
    y = number,
    group = 1
)) +
    geom_point() +
    geom_line() +
    xlab("Week of the year") +
    ylab("Number of sessions") +
    scale_y_continuous(
        breaks = seq(0, max(by_week$number) + 1, by = 1),
        limits = c(0, max(by_week$number) + 1)
    ) +
    facet_grid(type ~ .) +
    theme_dark(base_size = 20) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Finally, we can check if the overall number of help requests we've attended as the weeks have gone by.

```{r "graph_total", echo = FALSE, warning = FALSE, message = FALSE}
## Plot by week of the year ignoring guide
by_total <- summarise(by_guide_summary, number = sum(number))
ggplot(by_total, aes(
    x = paste0(year, '-', week),
    y = number,
    group = 1
)) +
    geom_point() +
    geom_line() +
    xlab("Week of the year") +
    ylab("Number of sessions") +
    scale_y_continuous(
        breaks = seq(0, max(by_total$number) + 1, by = 1),
        limits = c(0, max(by_total$number) + 1)
    ) +
    theme_dark(base_size = 20) + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## Could use this later once we have more data
# https://vuorre.netlify.app/post/2016/03/24/github-style-waffle-plots-in-r/

# logs_data$hours <- 0
# logs_data$day <- weekdays(logs_data$date, TRUE)
# 
# gh_waffle(logs_data)
```

These graphs are partially based on [`lcolladotor/mphtasessions`](https://github.com/lcolladotor/mphtasessions/blob/gh-pages/index.Rmd).
